### 2017-11-26 paper/sections/1_introduction.tex
paper: addresses #40
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

The biggest challenge for ParSplice is properly sizing the caches in the
storage hierarchy.  The memory usage for a single cache that stores molecule
coordinates is shown in Figure~\ref{fig:cache-management}, where the thin solid
lines marked with \(\times\)'s are the existing configurations in ParSplice.
The default configuration uses an unlimited sized cache, shown by the ``No
Cache Management" line, but using this much memory for one cache is
unacceptable for HPC environments, where a common goal is to keep memory for
such data structures below 3\%\footnote{Anecdotally, we find this threshold
works well for HPC applications.  For reference, a 1GB cache for a distributed
file system is too large in LANL deployments.}. Since ParSplice deploys a cache
per 300 worker processes, large simulations will not scale.  Users can
configure ParSplice to evict data when the cache reaches a threshold but this
solution requires tuning and parameter sweeps; the ``Cache (too small)" curve
in Figure~\ref{fig:cache-management} shows how a poorly configured cache can
save memory but at the expense of performance.  Even worse, this threshold
changes with different initial configurations and clusters so tuning needs to
be done for all system permutations.  Our dynamically sized cache, shown by the
think line in Figure~\ref{fig:cache-management}, detects key access patterns
and re-sizes the cache accordingly.  Without tuning or parameter sweeps, our
solution saves more memory than a hand-tuned cache with a negligible
performance degradation (within the baseline's standard deviation) and works
for a variety of initial conditions.

% What is Mantle
To design more flexible cache management policies, like our solution in
Figure~\ref{fig:cache-management}, we use the data management language and
policy engine from the Mantle paper~\cite{sevilla:sc15-mantle}.  Mantle was
originally touted as a programmable file system metadata load balancer, but we
realize now that the collection of abstractions was a control plane that
improved metadata access. So in this paper we refer to Mantle as a policy
engine that injects policies written in our data management language directly
into a running service, such as a file system or key-value store.  Rather than
co-designing a policy directly into the service, which requires domain-specific
knowledge to find and change policies, we expose the policies in a general way
so even developers unfamiliar with the domain can deploy quickly deploy solutions.
We show that our framework:

>>>>

The biggest challenge for ParSplice is properly sizing the caches in the
storage hierarchy.  The memory usage for a single cache that stores molecule
coordinates is shown in Figure~\ref{fig:cache-management}, where the thin solid
lines marked with \(\times\)'s are the existing configurations in ParSplice.
The default configuration uses an unlimited sized cache, shown by the ``No
Cache Management" line, but using this much memory for one cache is
unacceptable for HPC environments, where a common goal is to keep memory for
such data structures below 3\%\footnote{Anecdotally, we find this threshold
works well for HPC applications.  For reference, a 1GB cache for a distributed
file system is too large in LANL deployments.}. Since ParSplice deploys a cache
per 300 worker processes, large simulations will not scale.  Users can
configure ParSplice to evict data when the cache reaches a threshold but this
solution requires tuning and parameter sweeps; the ``Cache (too small)" curve
in Figure~\ref{fig:cache-management} shows how a poorly configured cache can
save memory but at the expense of performance, which is shown by the
annotation.  Even worse, this threshold changes with different initial
configurations and clusters so tuning needs to be done for all system
permutations.  Our dynamically sized cache, shown by the think line in
Figure~\ref{fig:cache-management}, detects key access patterns and re-sizes the
cache accordingly.  Without tuning or parameter sweeps, our solution saves more
memory than a hand-tuned cache with a negligible performance degradation
(within the baseline's standard deviation) and works for a variety of initial
conditions.

% What is Mantle
To design more flexible cache management policies, like our solution in
Figure~\ref{fig:cache-management}, we use the data management language and
policy engine from the Mantle paper~\cite{sevilla:sc15-mantle}.  While Mantle
was designed for the narrow purpose of filesystem metadata load balancing, this
paper provides evidence that the approach is more broad.  Specifically, the
collection of abstractions in Mantle provides a general control plane that
improves the performance of metadata access. So in this paper we refer to
Mantle as a policy engine that injects policies written in our data management
language directly into a running service, such as a file system or key-value
store.  Rather than co-designing a policy directly into the service, which
requires domain-specific knowledge to find and change policies, we expose the
policies in a general way so even developers unfamiliar with the domain can
deploy quickly deploy solutions.  We show that our framework:

### 2017-11-26 paper/sections/5_file-systems.tex
paper: addresses #40
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

>>>>

These similarities among effective policies for two very different domains
suggests that the heuristics and techniques in other load balancers can be used
for cache management. This generalization may reduce the work that needs to be
done for cache management as ideas may have already been explored and could
work ``out-of-the-box".
